### 2019-10-17 manuscript/manuscript.rmd
working on matrix_overlap figure

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE,
	echo=FALSE,
	dpi=300,
	cache=FALSE
	)
```

@@

# A colorblind friendly palette from http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/#a-colorblind-friendly-palette:
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

@@

```{r matrix_overlap}

matrix_overlap_rectangles = 
	lapply(sequence_matrices, function(x) lapply(sequence_matrices, function(y) overlap_rects(x,y))) %>% 
	unlist(recursive=FALSE) %>% 
	bind_rows()

ggplot(data=matrix_overlap_rectangles) + 
	scale_x_continuous(name="x") + 
	scale_y_continuous(name="y") +
	geom_rect( mapping=aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=MSA ), alpha=0.5) + 
	facet_grid( matrix_1 ~ matrix_2 )

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE,
	echo=FALSE,
	dpi=300,
	cache=FALSE,
	fig.width=8
	)
```

@@

# A colorblind friendly palette from http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/#a-colorblind-friendly-palette:
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#000000")

@@

```{r matrix_overlap}
sequence_matrices_nosub = sequence_matrices[sapply(sequence_matrices, function(x) !grepl('only|subsam', x@matrix_name))]
matrix_overlap_rectangles = 
	lapply(sequence_matrices_nosub, function(x) lapply(sequence_matrices_nosub, function(y) overlap_rects(x,y))) %>% 
	unlist(recursive=FALSE) %>% 
	bind_rows()

ggplot(data=matrix_overlap_rectangles) + 
	scale_x_continuous(name="x") + 
	scale_y_continuous(name="y") +
	geom_rect( mapping=aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=MSA ), alpha=0.5) + 
	facet_grid( matrix_1 ~ matrix_2 ) +
  theme_void() +
  theme(
    strip.background = element_rect(fill = "lightgrey"),
    strip.text.x = element_text(size = 8),
    panel.background = element_rect(fill ="#f9f9f9"),
  )
